A Switching Planner for Combined Task and Observation Planning

### 2011-02-09 subarchitectures/planner.sa/trunk/src/latex/AAAI11/evaluation.tex
new evaluation text from RIchard

We have implemented our switching approach in the MAPSIM
environment~\cite{brenner:nebel:jaamas09},
using \system{dlib-ml}~\cite{king:2009} for belief
revision. Sequential sessions use a modified version of Fast
Downward~\cite{fast-downward}, and DT sessions use our own contingent
procedure. We also implemented a simple dual-mode replanning {\em
baseline} approach. Here, when a switching action is scheduled for
execution the DT session applies a single entropy reduction action,
whose execution can provide evidence regarding the truth value of a
{\em relevant} assumption.
%%
%%  -- i.e,. we say a fact can
%% be directly sensed, if there is a DTPDDL {\em sense} declaration that
%% mentions the fact in its precondition. 
%%
Control is then immediately
returned to a new sequential session.

@@

Our evaluation examines DT sessions with initial belief-states
admitting between 20 and 100 abstract states with non-zero
probability. We run 50 simulations in each configuration, and have a
timeout on each simulation of 30 minutes (1800 seconds)\footnote{All
experiments were conducted on a 2.66GHz Intel Xeon X5355 using one CPU
core.}. The continual planning times are reported in
Figure~\ref{fig:results-time}, and the quality data in
Figure~\ref{fig:results-quality}.
%%
For each task, the goal is to find one or more objects and report
their position to a user. Usually there is a non-zero probability that
no plan exists, as the desired object might not be present in the
environment.
% MOG: I didn't do  evaluations for those, so let's remove them
% Item~$f$ reports for tasks requiring indirect sensing,
% where the robot must relocate to a room with a particular category
% (e.g. kitchen). the {\em baseline} is not able to complete Item~$f$,
% so is omitted from that reporting.  
In these experiments we only allocate reward on the achievement of all
goals, therefore we find it intuitive to report average plan costs and
the success rates in problems that admit a complete solution (i.e.,
positive reward scaled by a constant factor). The exception occurs for
items f and g of Figure~\ref{fig:results-quality}, where we report the
overall success rate of the respective approaches.

>>>>

We have implemented our switching approach in the MAPSIM
environment~\cite{brenner:nebel:jaamas09},
using \system{dlib-ml}~\cite{king:2009} for belief
revision. Sequential sessions use a modified version of Fast
Downward~\cite{fast-downward}, and DT sessions use our own contingent
procedure. Since most of the problems we consider are much larger than
any available DT planner can solve, for comparison purposes we also
implemented a simple dual-mode replanning {\em baseline}
approach. Here, when a switching action is scheduled for execution the
DT session applies a single entropy reduction action, whose execution
can provide evidence regarding the truth value of a {\em relevant}
assumption.
%%
%%  -- i.e,. we say a fact can
%% be directly sensed, if there is a DTPDDL {\em sense} declaration that
%% mentions the fact in its precondition. 
%%
Control is then immediately
returned to a new sequential session.

@@

Our evaluation examines DT sessions with initial belief-states
admitting between 20 and 100 abstract states with non-zero
probability. We run 50 simulations in each configuration, and have a
timeout on each simulation of 30 minutes (1800 seconds)\footnote{All
experiments were conducted on a 2.66GHz Intel Xeon X5355 using one CPU
core.}. The continual planning times are reported in
Figure~\ref{fig:results-time}, and the quality data in
Figure~\ref{fig:results-quality}.
%%
For each task, the goal is to find one or more objects and report
their position to a user. Usually there is a non-zero probability that
no plan exists, as the desired object might not be present in the
environment.
% MOG: I didn't do  evaluations for those, so let's remove them
% Item~$f$ reports for tasks requiring indirect sensing,
% where the robot must relocate to a room with a particular category
% (e.g. kitchen). the {\em baseline} is not able to complete Item~$f$,
% so is omitted from that reporting.  
In these experiments we only allocate reward on the achievement of all
goals, therefore we find it intuitive to report average plan costs and
the success rates in problems that admit a complete solution (i.e.,
positive reward scaled by a constant factor). The exception occurs for
items f and g of Figure~\ref{fig:results-quality}, where we report
expected discounted rewards (not plan costs).
